30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-14 paper.tex
Added the table to the paper
Please work in the table in the paper from now on :)

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load, see original template for descriptions)
%\usepackage{ifpdf}
%\usepackage{cite}
%\usepackage[cmex10]{amsmath}
%\usepackage{algorithmic}
%\usepackage{array}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
%\usepackage{dblfloatfix}
%\usepackage{url}
\usepackage{graphicx}
\usepackage{epstopdf}

@@

>>>>

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load, see original template for descriptions)
%\usepackage{ifpdf}
%\usepackage{cite}
%\usepackage[cmex10]{amsmath}
%\usepackage{algorithmic}
%\usepackage{array}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
%\usepackage{dblfloatfix}
%\usepackage{url}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{caption}

@@

\begin{center}
	\captionof{table}{A comparison of decentralized peer-to-peer overlay networks}
    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | p{2cm} |}
    \hline
    	Name & Year & Compatible with Tor & Public implementation & Used in practice & Attack resistance & Provides anonymity \\ \hline
	Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline
	Freenet & 2001 & no & yes, implementations are based on the FCP (Freenet Client Protocol) & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & yes\\ \hline
	Tapestry & 2001 & no & yes & yes, several applications are based on it such as OceanStore and Bayeux & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
	Pastry & 2001 & no & yes & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
	Anonymizing peer-to-peer proxy (AP3) & 2004 & no & no & no & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & yes\\ \hline
	Tarzan & 2002 & no & no(?) & no & ? & yes\\ \hline
	MorphMix & 2002 & no & yes & no & yes, although depending on the number of colluding malicious nodes & yes\\ \hline
	I2P & 2003 & no & yes & yes & ? & yes\\ \hline
	Salsa & 2006 & no & ? & ? & ? & ?\\ \hline
	Tribler & 2008 & no, based on BitTorrent & yes & yes & ? & not yet\\ \hline
	Torks & 2009 & yes & implementation exists, but not public(?) & no & ? & yes\\ \hline
	NISAN & 2009 & no & no & no & ? & yes\\ \hline
    \end{longtable}
\end{center}
